%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
\usepackage{url}

%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Ankit Singh} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 2pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{Systems Engineer} % Your address
\moveleft.5\hoffset\centerline{(+91)~9465096506}
\moveleft.5\hoffset\centerline{iam.ankit@yahoo.in}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
\section{OBJECTIVE}  
To work in a challenging and prolific environment that demands all my skills and efforts in various fields and helps me to build up constructively and to excel in my field through hard work, dedication and perseverance.


%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERIENCE}
{\sl \textbf{Infosys limited}} \hfill August 2016 - Present \\
Systems Engineer
\begin{itemize}
\item Software Developer with hands on experience in Java, JavaScript and UI Designing.  
\item Undergone generic training in Python, Database along with Foundation training in Java and web technologies.
\item Completed a POC on ELK(Elasticsearch, Logstash, Kibana) stack to build a real time dashboard solution.
\item Performed development activities including designing, implementation and testing in Agile Environment.  
\item 	Handling client communications and functional discussions with the onsite Business Analysts and product owners and delivering demos of developed modules.  
\item Certified MuleSoft Developer - Integration and API Associate (Mule 3.8).   
\end{itemize} 
{\sl\textbf{Science \& Tech. Entrepreneur’s Park}} \hfill August 2015 - Dec 2015 \\
	Java Developer Intern 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item 	Worked on a Web application (Exam system) developed from scratch. 
\item 	Technology Used: Java, HTML, CSS, JavaScript, MySQL.
\end{itemize}


%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{TECHNOLOGY \\ SKILLS} 
{\sl \textbf{Programming Languages:}} Java. \\
{\sl \textbf{Web Related:}} HTML, CSS, Bootstrap, JavaScript, AJAX.  \\
{\sl \textbf{Database:}} MySQL, Oracle.   \\
{\sl \textbf{Other Skills:}} Elasticsearch, RESTful web services, Junit.  \\
{\sl \textbf{Also Worked On:}} JSP, Servlet, AngularJS.   \\
{\sl \textbf{Operating Systems:}} Windows, Linux.   \\
{\sl \textbf{Tools:}} Eclipse, Anypoint Studio.
 
%----------------------------------------------------------------------------------------
%	PROJECT EXPERIENCE
%----------------------------------------------------------------------------------------
 
\section{PROJECT EXPERIENCE}
{\sl \textbf{Attach}} \hfill  \\
\textbf{Client - CISCO} \\
\textbf{\textit{Description}}: The purpose of this project is to update an Existing case.   \\
\textbf{\textit{Environment and Technologies}}: Java, Apache James 3.0, SSH Tectia, Eclipse,SVN \\
\textbf{\textit{Roles \& Responsibilities}}:  
\begin{itemize}
\item	Upgradation of James server from 2.3 to 3.0.  
\item	Created Mailets for processing of emails in Java.  
\item	Configured and Deployed project on different environment.  
\item Involved in testing, debugging of the complete flow of the modules.   
\end{itemize} 

{\sl \textbf{NPS (New Product Information)}} \hfill  \\
\textbf{Client - CISCO} \\
\textbf{\textit{Description}}: The purpose of this project is to manage and update the product and order information for newly added or existing products.     \\
\textbf{\textit{Environment and Technologies}}: Java, JSP, JavaScript, Eclipse, SVN \\
\textbf{\textit{Roles \& Responsibilities}}:  
\begin{itemize}
\item	Added functionalities for better user experience in JavaScript.  
\item	Validated and enhanced product performance.  
\item	Involved in testing and debugging the flow of the modules.   
\item	Project involved Agile Software Development Life Cycle.    
\end{itemize}  
{\sl \textbf{Infy - Retail }} \hfill  \\
\textbf{\textit{Description}}: A retail enterprise solution, which offers variety of plans to retailers. End users can see top customers based on region, any customers can upgrade or downgrade their plan.  Customers will be awarded based on their purchase.       \\
\textbf{\textit{Environment and Technologies}}: Java, RESTful web services, AngularJS, Ajax, Hibernate, Eclipse, Git      \\
\textbf{\textit{Roles \& Responsibilities}}: 
\begin{itemize}
\item	Created responsive UI for the application.  
\item	Implemented functionalities to extract top ten customers.  
\item	Created filters such as date range and amount spent for search results.  
\item	Designed and developed the processes using web-services.
\item	Implemented functionality for user to change his plan based on certain parameters.  

  
\end{itemize} 
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%---------------------------------------------------------------------------------------- 

\section{EDUCATION} 
{\sl \textbf{Bachelor of Technology (B.Tech)}} in Computer Science and Engineering from Guru Nanak dev Engineering college, Ludhiana with 73\%  in 2016.\\
{\sl \textbf{Higher Secondary school Certification (12th)}} from Gopeshwar College, Hathua with 66\% in 2011.\\
{\sl \textbf{High school Certification (10th)}} from M.M.H High School, Gopalganj with 83.6\% in 2009.
%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------
\section{OTHER-\\ ACTIVITIES} 
\begin{itemize}
\item Cleared Infosys Foundation training in High performance band (89\%).
\item Won academic award for securing 1st in district in 10th board. 
\item Consistently been in Top 3 of class from 1st-10th. 
\item Certified DRR (Disaster Recovery Representatives). 
\item Actively participated and won prizes in cultural and social events like Nukkad Natak, Skits, Poster Making, Aptitude, Mathematic Competitions etc.
\item Successfully Completed web technologies course on Udemy. 
\end{itemize}
%----------------------------------------------------------------------------------------
%	PROFILES SECTION
%---------------------------------------------------------------------------------------- 
\section{PERSONAL DETAILS} 
{\sl \textbf{Date of Birth :}} February 8th, 1994 \\
{\sl \textbf{Sex :}} Male \\
{\sl \textbf{Nationality :}} Indian \\
{\sl \textbf{Languages Known :}} English, Hindi \\
{\sl \textbf{Github :}} \url{https://github.com/singhankit} \\
{\sl \textbf{LinkedIn :}} \url{https://www.linkedin.com/in/ankit-singh-027b20b2/}

\end{resume}
\end{document}